---
title: "Spatial analyst"
format: 
  html:
    code-fold: true
    code-tools: true
---

So let's pratice !!!

## Spatial analyst:

  Now let's start with data contains the information of longitude and latitude of customer's locations. Member install data [optimize](index.qmd) before.

```{r}
#| include: false
#| echo: false
library(readxl)
optimize<-read.csv(r"(C:\\Users\\locca\\Documents\\Xuân Lộc\\VILAS\\Final project\\Optimize_df.csv)")

## Call packages:
pacman::p_load(rio,
               here,
               janitor,
               tidyverse,
               dplyr,
               magrittr,
               ggplot2,
               purrr,
               lubridate,
               knitr,
               shiny)
```

```{r}
#| echo: true
#| message: false

#New manufacter:
new_manufacter= data.frame(
  Customers = str_c(rep("Manufacter"),1:3),
  Latitude =c(21.12256201,21.68421,20.34250),
  Longitude = c(105.9150683,105.1940,106.2946),
  Total.transactions = c(0,0,0),
  Inventory = c(3000,2000,2500))

route<-rbind(new_manufacter,
             optimize%>% select(Customers,
                                Longitude,
                                Latitude,
                                Total.transactions) %>% 
               mutate(Inventory = round(runif(50,100,400)))
)

colnames(route)[4]<-"Demand"

route$Node<-1:nrow(route)

## Adding status:
route$Status <- ifelse(route$Inventory - route$Demand > round(mean(route$Demand)/2),"Control",ifelse(route$Inventory- route$Demand  > 0,"Warning","Outstock" ))

```

  So we have enough data to pratice. Let show this data in map for clearly understading.
  
### Map of supply chain management

```{r}
#| fig-cap: "The location of all customers and internal manufacters"
#Prepare labels:
labels<- paste0("<strong> Customers </strong> ",
               route$Customers, "<br/> ",
               "<strong> Inventory: </strong> ",
               route$Inventory, "<br/> ",
               "<strong> Demand </strong> ",
               route$Demand, "<br/> ",
               "<strong> Status </strong> ",
               route$Status, "<br/> ") %>% 
         lapply(htmltools::HTML)

library(leaflet)
library(fontawesome) 
#If you don't have, try to install by: devtools::install_github("rstudio/fontawesome")
logos <- awesomeIconList(
  Customer = makeAwesomeIcon(
    icon = "home",
    iconColor = "white",
    markerColor = "blue",
    library = "fa"),
  Manufacter = makeAwesomeIcon(
    icon = "beer",
    iconColor = "gold",
    markerColor = "black",
    library = "fa")
)

#Prepare the logos:
route$ticker<-c(rep("Manufacter",3),
                rep("Customer",
                    nrow(route)-3))

leaflet(data = route) %>% 
  addTiles() %>%
  addAwesomeMarkers(
             lng = ~Longitude, 
             lat = ~Latitude, 
             label = ~labels,
             icon = ~logos[ticker]) %>% 
  setView(lng = mean(route$Longitude), 
          lat = mean(route$Latitude),
          zoom = 7) 
```

  In the following code, I want to emphasize that the names of colors should have the first letter capitalized. For example, use "Red" instead of "red".
  
  You might be wondering why this is important, and I had the same question :)). After some online research, I found a response to a similar question about changing the color of markers in R using Leaflet [Leaflet change color of markers (R)](https://stackoverflow.com/questions/71726478/leaflet-change-color-of-markers-r). 
  
  It was mentioned that capitalizing the first letter allows R to color the markers based on different factors. If you don't capitalize the first letter, R will color the markers randomly (I'm not sure why).

```{r}
#| fig-cap: "The mini map by clustering the locations"
#Setting the level of status
route$Status<-fct_relevel(route$Status,"Control","Warning","Outstock")

#Prepare palette for labeling control/warning/outstock:
palPwr <- leaflet::colorFactor(palette = c("Lightgreen","Yellow","Red"), 
                               domain = route$Status,
                               ordered = T)

#Prepare font for labeling
font<-labelOptions(noHide = T, 
                  direction = "bottom",
                  style = list(
        "font-family" = "serif",
        "font-style" = "ilatic",
        "box-shadow" = "3px 3px rgba(0,0,0,0.25)",
        "font-size" = "10px",
        "border-color" = "rgba(0,0,0,0.5)"
      ))

#Plot map with leaflet:
library(leaflet.extras)
leaflet(data = route) %>% 
  addProviderTiles("CartoDB.Positron") %>% 
  addCircleMarkers(radius = 10, # size of the dots
                   fillOpacity = .7, # alpha of the dots
                   stroke = FALSE, # no outline
                   label = ~labels,
                   lng = ~Longitude, 
                   lat = ~Latitude, 
                   color = ~palPwr(route$Status),
                   clusterOptions = markerClusterOptions(),
                   labelOptions = font) %>% 
  leaflet::addLegend(position = "bottomright",
            values = ~Status, # data frame column for legend
            opacity = .7,
            pal = palPwr, # palette declared earlier
            title = "Status") %>%   # legend titleƯ
  addResetMapButton()
```

  Also for adjusting the base map, you can base on the preview of base map in [Leaflet preview](https://leaflet-extras.github.io/leaflet-providers/preview/) and copy the name of provider to paste in the argument {addProviderTitles}. For instance, I use provider = `CartoDB.Positron`.

## Routing the vehicle's path for Supply Chain Plan:

To set up the connection between RStudio and GitHub, you can use the `source()` function and assign the URL link of the GitHub repository that contains the R script you need. Remember to click on "Raw" to move to another page and then copy that URL.

I found the original code in Viktor Plamenov's project on [GitLab](https://gitlab.com/vikplamenov/vrpoptima/-/tree/main/R?ref_type=heads). I found it convenient to use, so I copied and uploaded it to my private GitHub repository. You can use this URL for your work.

The author created the package {vrpoptima} for easily install and using it. You can install by package {remote}, another details you can read in this link [remotes](https://remotes.r-lib.org/reference/install_gitlab.html)

```{r}
#| include: false
#| warning: false
#| message: false
# Repo must in format username/repo[@ref].
remotes::install_gitlab("vikplamenov/vrpoptima")
```

```{r}
#| warning: false
#| message: false
library(vrpoptima)
colnames(optimize)[2:3]<-c("lat","lon")
colnames(new_manufacter)[2:3]<-c("lat","lon")

mat_optimize<-as.matrix(optimize[,2:3])

dist_optimize<-as.matrix(geodist::geodist(mat_optimize,measure = 'haversine')/1000)

mat_WH<-as.matrix(new_manufacter[,2:3])
```

Next, just simply add the criteria and run the code illustrated below.

```{r}
#| warning: false
#| echo: false
#Optimizing:
(solution <-  VehicleRouting(visit_points = mat_optimize,
                           num_agents = nrow(new_manufacter),
                           agent_points = as.matrix(new_manufacter[,2:3]),
                           cost_type = 2,
                           max_tour_distance = 250000,
                           max_tour_visits = 30,
                           distance_metric = 'Geodesic',
                           distance_matrix = dist_optimize,
                           min_tour = 2,
                           population_size = 96,
                           num_generations = 1000, 
                           distance_truncation = TRUE, 
                           seed = 42)
)

```

Finally, plot the results of optimization by two functions:

*   `PlotToursCombined` function: use to display of the combined routes created with the genetic program.

*   `PlotToursIndividual` function: use to display of the individual routes created with the genetic program.

```{r}
#Plot the results:
routes <- solution$routes
rownames(routes) <- 1:nrow(routes)
routes_list = RoutesDataPrep(routes = solution$routes, 
                             visit_points = mat_optimize, 
                             agent_points = as.matrix(new_manufacter[,2:3]))


# Display all routes at the same time
PlotToursCombined(solution = solution, 
                  routes_list = routes_list,
                  agent_locations = as.matrix(new_manufacter[,2:3]),
                  orientation = "vertical")

# Display all the inidividual routes on a single figure block
PlotToursIndividual(solution = solution, 
                    routes_list = routes_list)
```

# References:

Thanks to all authors of documentaions below that help me complete this pratice.

* [leaflet](https://www.jla-data.net/eng/leaflet-in-r-tips-and-tricks/) by Jindra Lacko.

* [How to Use Git/GitHub with R](https://rfortherestofus.com/2021/02/how-to-use-git-github-with-r) by David Keyes.

* [Multiple Depot in VRP](https://gitlab.com/vikplamenov/vrpoptima/-/blob/main/R/VehicleRouting.R?ref_type=heads) by Viktor Plamenov.

* [htmltools with R](https://3mw.albert-rapp.de/) by Albert Rapp.

* [Dataui](https://timelyportfolio.github.io/dataui/articles/dataui_reactable.html)